---
title: "Daniel Anderson's Vita"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [anderson-cv.css]
    number_sections: false
links-to-footnotes: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

#### cv entries #####
cv_entries <- readxl::read_xlsx(here::here("data", "cv_entries.xlsx"))

#### publications #####
pubs <- readxl::read_xlsx(here::here("data", "pubs.xlsx")) %>% 
  arrange(order) %>% 
  select(-order)

pubs <- map_df(pubs, ~gsub("\\.$", "", .x))

courses <- readxl::read_xlsx(here::here("data", "courses.xlsx"))
```


```{r}
PDF <- TRUE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
if(PDF) {
  header <- '
  <a style = "color:#808080" href="https://datalorax.github.io/anderson-cv/" class="icon-block">
      View online
  </a>
  <i style = "color:#808080" class="fas fafooter fa-globe"></i>
  '
} else {
  header <- '
  <a style = "color:#808080" href="https://github.com/datalorax/anderson-cv/raw/master/anderson-cv.pdf">
    Download PDF
  </a>
  <i style = "color:#808080" class="fas fa-download"></i>
  '
}
```


<div class = "download">
```{r results = "asis"}
cat(header)
```

</div>

<div class = "footer",>
  <a href="https://github.com/datalorax/" class="icon-block">
      <i class="fab fafooter fa-github"> | </i>
  </a>
  
  <a href="mailto:daniela@uoregon.edu" class="icon-block">
      <i class="fas fafooter fa-envelope"> | </i>
  </a>
  
  <a href="https://www.datalorax.com" class="icon-block">
      <i class="fas fafooter fa-globe"> | </i>
  </a>
  
  <a href="(https://twitter.com/datalorax_" class="icon-block">
      <i class="fab fafooter fa-twitter"> | </i>
  </a>
  
  <a href="(https://orcid.org/0000-0003-4699-4680" class="icon-block">
      <i class="fab fafooter fa-orcid"></i>
  </a>
  
</div>


<div id = "block_container">

<div class = "first", id="bloc1">Daniel</div>  
<div class = "last", id="bloc2">Anderson</div>

</div>

<div id = "position", class = "position">
Research Assistant Professor
</div>


<div id = "sub", class = "sub">
Curriculum Vita
</div>


<div class="grid-container">

```{r summary, child = here::here("content", "summary.Rmd")}
```

```{r contact-info, child = here::here("content", "contact-info.Rmd")}
```

</div>

## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what)
         ) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Brief professional history {.history .nohead}

```{r}
cv_entries %>% 
  filter(type == 'history') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

## Additional training (received) {.nohead .extratrain}

<div class = "hangingindent">
```{r}
cv_entries %>% 
  filter(type == "extra-training") %>% 
  mutate(training = paste0(what, " (", year_end, "). ", where, "\\n")) %>% 
  select(training) %>% 
  kable()
```
<div/>

# Teaching

<div class = "inote">
Icons link to additional content  
</div>

## Data science specialization {.nohead .tch}
I have led the design, development, and teaching of a new [five-course graduate-level data science specialization](https://github.com/uo-datasci-specialization) offered through the University of Oregon's College of Education. The following lists the sequence of courses in the specialization, as well as the year/quarter in which I have taught the courses.

```{r}
courses %>% 
  filter(type == "ds") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website),
                         paste0(
                           '[<i class="fas falink fa-globe"></i>](',
                           website,
                           ')'
                         ),
                         ""),
         fa_git = ifelse(!is.na(repo),
                         paste0(
                           '[<i class="fab falink fa-github"></i>](',
                           repo,
                           ')'
                         ),
                         ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""), 
                         credits, " credit hours.<sp>Sl</sp>",
                         fa_git, "<sp>Sl</sp>", fa_web),
         order = paste0(order, ".")) %>%
  select(order, course) %>%
  kable()
```

## Additional courses taught {.nohead .tch}

```{r}
courses %>% 
  filter(type == "other") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab fafooter fa-github"></i></a>'),
                         ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""),
                         credits, " credit hours.",
                         "<sp>Sl</sp>", fa_git, "<sp>Sl</sp>", fa_web),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()
```

## Related experience {.nohead .tch}

```{r}
courses %>% 
  filter(type == "related") %>% 
  arrange(order) %>% 
  mutate(fa_web = ifelse(!is.na(website), 
                         paste0( '<a href=', 
                                 website, 
                                 '><i class="fas falink fa-globe"></i></a>'),
                         ""),
         fa_git = ifelse(!is.na(repo), 
                         paste0('<a href=', 
                                repo, 
                                '><i class="fab fafooter fa-github"></i></a>'),
                         ""),
         crn = ifelse(!is.na(crn), paste0("CRN: ", crn, "; "), ""),
         credits = ifelse(!is.na(credits), 
                          paste0(credits, " credit hours."),
                          ""),
         course = paste0("*", title, "*. (", quarter, ", ",  year, "). ", 
                         crn, credits, 
                         "<sp>Sl</sp>", fa_git, "<sp>Sl</sp>", fa_web),
         course = gsub("NA, ", "", course),
         order = paste0(order, ".")) %>% 
  select(order, course) %>% 
  kable()
```

<br class="pageBreak"/>

# Scholarship

<div class = "inote">
Icons link to additional content  
</div>

## Peer-Reviewed Publications

```{r}
make_cite <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL,
                      version = NULL,...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(annual_meeting) {
       conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
      }
    }
    else {
       if(annual_meeting) {
          conference <- paste0("Paper presented at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Paper presented at the ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".") 
      }
    }
  }
  if(!is.null(version)) {
    version <- paste0("R package version ", version, ".")
  }
  authors <- gsub(
    "Anderson, D\\.?",
    "<span style= 'font-weight: 500'>Anderson, D.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, "."),
        version, 
        conference,
        journal, 
        volume,
        book,
        pages, 
        doi,
        place_published)
}

prpas <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prpas, seq_len(nrow(prpas)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prpas$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prpas$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prpas$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prpas$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prpas$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)
```

<div class = "hangingindent prpa nohead">

```{r} 
kable(pubs_tbl)
```

</div>


<!-- ## Manuscripts under review for publication {.submitted .nohead} -->

<!-- <div class = "hangingindent"> -->

<!-- ```{r } -->
<!-- submitted <- pubs %>%  -->
<!--   filter(type == "in-review") %>%  -->
<!--   select(-type) -->

<!-- fa_doc <- ifelse( -->
<!--   !is.na(submitted$full_paper_link),  -->
<!--   paste0('[<i class="fas falink2 fa-file-alt"></i>](',  -->
<!--          submitted$full_paper_link,  -->
<!--          ")" -->
<!--          ), -->
<!--   "" -->
<!--   ) -->

<!-- fa_git <- ifelse( -->
<!--   !is.na(submitted$git_repo),  -->
<!--   paste0('[<i class="fab falink2 fa-github"></i>](',  -->
<!--          submitted$git_repo,  -->
<!--          ")" -->
<!--          ), -->
<!--   "" -->
<!--   ) -->

<!-- each_cite <- split(submitted, seq_len(nrow(submitted))) -->
<!-- empties <- map(each_cite, ~map_lgl(.x, is.na)) -->

<!-- cites <- map2(each_cite, empties, ~.x[ ,!.y]) -->
<!-- formatted_cites <- map(cites, ~do.call(make_cite, .x))  -->

<!-- if(length(formatted_cites) > 0) { -->
<!--  submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."), -->
<!--                          cites = paste(unlist(formatted_cites), fa_doc, fa_git))  -->

<!--   kable(submitted_tbl)  -->
<!-- } -->
<!-- ``` -->

<!-- </div> -->


## Book chapters {.submitted .nohead}

<div class = "hangingindent">

```{r}
chapters <- pubs %>% 
  filter(type == "book-chapter") %>% 
  select(-type)

each_cite <- split(chapters, seq_len(nrow(chapters)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

chapters_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                        cites = unlist(formatted_cites)) 
  
kable(chapters_tbl)

```

</div>

<br class="pageBreak">

## National & International Conference Presentations {.prpa .nohead}

<div class = "hangingindent">

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git)
)
  

conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

kable(conf_tbl)
```

</div>


## Regional conferences {.nohead .submitted}

<div class = "hangingindent">

```{r}
regional <- pubs %>% 
  filter(type == "regional") %>% 
  select(-type)

fa_pres <- ifelse(
  !is.na(regional$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         regional$slides_link, 
         ")"
         ),
  ""
  )

each_cite <- split(regional, seq_len(nrow(regional)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

regional_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                       cites = paste(unlist(formatted_cites), fa_pres)) 
  
kable(regional_tbl)
```

</div>

## Technical reports (selected) {.submitted .nohead}
I am a co-author on over [sixty](https://www.brtprojects.org/publications/technical-reports/) technical reports. Below is a sample of 10 that are among the most cited.

<div class = "hangingindent">

```{r}
trs <- pubs %>% 
  filter(type == "tr") %>% 
  mutate(title = paste0("*", title),
         title = gsub("\\s\\(Tech", "\\* \\(Tech", title),
         place_published = paste0(place_published, ".")) %>% 
  select(-type)



fa_doc <- ifelse(
  !is.na(trs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         trs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(trs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         trs$git_repo, 
         ")"
         ),
  ""
  )

each_cite <- split(trs, seq_len(nrow(trs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

submitted_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                        cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 
  
kable(submitted_tbl)
```

</div>


# External Funding Activity

<div class = "inote">
Icons link to additional content  
</div>

```{r}
grants <- readxl::read_xlsx(here::here("data", "grants.xlsx"))

make_grant_cite <- function(title, funding_agency, award_num, role, pi,
  date_start, date_end, budget, fte_low_range, fte_high_range, contract,
  link, in_review = FALSE, ...) {
  
  if(in_review) {
    budg <- paste0(". Proposed budget: $", 
                   prettyNum(budget, big.mark = ",")
                   )
  } else {
    budg <- paste0(". Total budget: $", 
                    prettyNum(budget, big.mark = ",")
                    )
  }
  funder <- paste0("*", funding_agency, "* ")
  if(!is.na(award_num)) {
    funder <- paste0(funder, " (Award #", award_num, ")")
  }
  if(fte_low_range != fte_high_range) {
    fte <- paste0("FTE: ", 
                  format(fte_low_range, nsmall = 2), 
                  " to ", 
                  format(fte_high_range, nsmall = 2),
                  " across project years.")
  }
  else {
    fte <- paste0("FTE: ", format(fte_low_range, nsmall = 2), ".")
  }

  cite <- paste0(paste0(title, ". "),
                 paste(month(date_start, label = TRUE, abbr = FALSE), 
                       year(date_start), 
                       "to",
                       month(date_end, label = TRUE, abbr = FALSE), 
                       year(date_end)),
                 ". ", funder, 
                 budg,
                 paste0(". ", 
                        "<span style= 'font-weight: 500'> Role: </span>", 
                        role, 
                        ". ")
                )
  cite <- ifelse(!is.na(pi), 
                 paste0(cite, " PI: ", pi, "."),
                 cite)
  icon <- ifelse(!is.na(link), 
                 paste('<a href=', 
                       link, 
                       '><i class="fas falink2 fa-globe"></i></a>'),
                 "")
  paste(cite, fte, icon)
}
```

## Under review {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants_submitted <- grants %>%
  filter(type == "in-review") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite)

kable(grants_submitted[1:2, ])
```

</div>


## Current projects {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants %>%
  filter(type == "current") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite) %>%
  kable()
```

</div>

<br class = "pageBreak"/>

## Completed projects {.nohead .submitted}

<div class = "hangingindent">

```{r}
grants %>%
  filter(type == "completed") %>%
  group_by(count = paste0(seq(1, nrow(.)), ".")) %>%
  nest() %>%
  mutate(cite  = map(data, ~do.call(make_grant_cite, .x))) %>%
  select(-data) %>%
  unnest(cite) %>%
  kable()
```

</div>


# Software development

<div class = "inote">
Icons link to additional content  
</div>

I am active in the R community and have developed a number of packages. My GitHub repositories for R rank in the [top 30 (of 8,590) nationally and top 100 (of 72,387) worldwide](http://git-awards.com/users/datalorax). Below is a summary of packages I have authored and contributed to, as well as a few interactive data applications.

## Author {.nohead .submitted}

```{r }
pkg_aut <- pubs %>% 
  filter(type == "software-aut") %>% 
  select(-type) 

each_cite <- split(pkg_aut, seq_len(nrow(pkg_aut)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_git <- ifelse(
  !is.na(pkg_aut$git_repo), 
  paste0('[<i class = "fab falink2 fa-github"></i>](', 
         pkg_aut$git_repo, 
         ")"
         ),
  ""
  )

fa_globe <- ifelse(
  !is.na(pkg_aut$full_paper_link), 
  paste0('[<i class = "fas falink2 fa-globe"></i>](', 
         pkg_aut$full_paper_link, 
         ")"
         ),
  ""
  )

pkg_aut_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                      cites = paste(unlist(formatted_cites), fa_git, fa_globe)) 

```


<div class = "hangingindent submitted nohead">

```{r software2}
kable(pkg_aut_tbl)
```

</div>


## Contributor {.nohead .submitted}

<div class = "hangingindent">

```{r }
pkg_ctb <- pubs %>% 
  filter(type == "software-ctb") %>% 
  select(-type) 

each_cite <- split(pkg_ctb, seq_len(nrow(pkg_ctb)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_git <- ifelse(
  !is.na(pkg_ctb$git_repo), 
  paste0('[<i class = "fab falink2 fa-github"></i>](', 
         pkg_ctb$git_repo, 
         ")"
         ),
  ""
  )

fa_globe <- ifelse(
  !is.na(pkg_ctb$full_paper_link), 
  paste0('[<i class = "fas falink2 fa-globe"></i>](', 
         pkg_ctb$full_paper_link, 
         ")"
         ),
  ""
  )

pkg_ctb_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                      cites = paste(unlist(formatted_cites), fa_git, fa_globe)) 
  
kable(pkg_ctb_tbl)  
```

</div>


## Web applications {.nohead .submitted}
In addition to the below, I have also developed interactive web applications and websites for non-profit and statewide agencies, which are generally password protected (and not directly shareable).

<div class="hangingindent web-apps">

```{r}
web_app <- pubs %>% 
  filter(type == "web-app") %>% 
  select(-type) 

each_cite <- split(web_app, seq_len(nrow(web_app)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_git <- ifelse(
  !is.na(web_app$git_repo), 
  paste0('[<i class = "fab falink2 fa-github"></i>](', 
         web_app$git_repo, 
         ")"
         ),
  ""
  )

fa_globe <- ifelse(
  !is.na(web_app$full_paper_link), 
  paste0('[<i class = "fas falink2 fa-globe"></i>](', 
         web_app$full_paper_link, 
         ")"
         ),
  ""
  )

web_app_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                      cites = paste(unlist(formatted_cites), fa_git, fa_globe)) 
  
kable(web_app_tbl)

```

</div>


# Professional Service 

## Working Committees {.nohead .submitted}

<div class = "hangingindent">
 
```{r}
committees <- cv_entries %>%
  filter(type == "service")

committees %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(paste0("*", what, "*"),
                       ". (", 
                       ifelse(!is.na(year_begin), 
                              paste0(year_begin, "-"), 
                              ""), 
                       year_end, 
                       "). ",
                       where, 
                       ".")) %>%
  select(count, cite) %>%
  kable()
```

</div>

## Doctoral committees {.nohead .submitted}

I have served on the following doctoral committee.

<div class = "hangingindent" style = "margin-top: -15px;">

```{r}
doc_stu <- cv_entries %>%
  filter(type == "doc-committee")

doc_stu %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(what, ". (", year_begin, "-", year_end, 
                       "). Dissertation title: *", additional_info, "*. ", 
                       where, ".")) %>%
  select(count, cite) %>%
  kable()

```

</div>

<br class = "pageBreak"/>

## Conference organization
I was the lead organizer of the 2020 [Cascadia R Conference](https://cascadiarconf.org), which included planned keynotes on open science and  machine learning, with presenters from academia (University of Washington) and industry, with machine learning engineers who use R in production with T-Mobile. The conference also included planned workshops on data visualization, reproducible and dynamic report generation with R Markdown (lead by doctoral students from my courses), interactive web application development with [shiny](https://shiny.rstudio.com), and introductory machine learning. Conference presenters were from around the Pacific Northwest, and an emphasis on gender and ethnic representation was emphasized when considering prospective presenters. The conference was canceled due to COVID-19.

## Workshops delivered{.nohead .submitted}

<div class = "hangingindent">

```{r}
workshops <- cv_entries %>%
  filter(type == "workshop-delivered")

workshops %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(paste0("*", what, "*"),
                       ". (", 
                       year_end, 
                       "). ",
                       where, 
                       ".")) %>%
  select(count, cite) %>%
  kable()
```

</div>


## Peer review service {.nohead}

I serve on the editorial review board for [Reading Research Quarterly](https://ila.onlinelibrary.wiley.com/journal/19362722) and have served as an ad hoc reviewer for the following journals:

<div class = "adhoc">

```{r}
reviewer <- cv_entries %>%
  filter(type == "peer-reviewer") %>%
  select(what) %>%
  mutate(index = c(rep(1, floor(nrow(.)/2)), 
                   rep(2, nrow(.) - floor(nrow(.)/2))
                   ))


jou1 <- reviewer$what[reviewer$index == 1]
jou2 <- reviewer$what[reviewer$index == 2]

if(length(jou1) < length(jou2)) {
  jou1 <- c(jou1, NA)
}
if(length(jou2) < length(jou1)) {
  jou2 <- c(jou2, NA)
}

data.frame(jou1, jou2) %>%
  kable()
```

</div>

In addition to these journals, I have served as a reviewer for the annual conferences for the [American Educational Research Association](https://www.aera.net) and the [Council for Exceptional Children](https://exceptionalchildren.org).

<!-- <br class="pageBreak"> -->

# Awards {.submitted .nohead}

<div class="hangingindent">

```{r}
cv_entries %>%
  filter(type == "award") %>%
  mutate(count = paste0(seq(nrow(.), 1), "."),
         cite = paste0(what, ". (", year_end, "). ", 
                       ifelse(!is.na(additional_info), 
                              paste0(additional_info, "."),
                              "")
                       )
        ) %>%
  select(count, cite) %>%
  kable()
```

</div>

# Professional Affiliations {.nohead .submitted}

<div class="hangingindent prof">

```{r}
cv_entries %>%
  filter(type == "affiliation") %>%
  mutate(count = paste0(seq(nrow(.), 1), ".")) %>%
  select(count, what) %>%
  kable()
```

</div>